\bf A Continuous-time Multicast \\Network Model

### 2018-04-25 paper/paper.tex
code in pkg format

\subsection{Posterior Predictive Checks}\label{subsubsec:PPC_email} 	   
Finally, we perform posterior predictive checks \cite{rubin1984bayesianly} to evaluate the appropriateness of our model specification for the Montgomery County email data and the threat and imposition of sanctions (TIES) data. We formally generated entirely new data, by simulating ties and timestamps $\{(a_{d}, \boldsymbol{r}_{d}, t_{d})\}_{d=1}^D$ from the genenerative process in Section \ref{sec:generative process}, conditional upon a set of inferred parameter values from the inference in Section \ref{sec:inference}. For the test of goodness-of-fit in terms of network dynamics, we use multiple network statistics that summarize meaningful aspects of the Montgomery County email data and the threat and imposition of sanctions (TIES) data: indegree distribution, outdegree distribution, recipient size distribution, time-increments distribution, the edgewise shared partner distribution, and the geodesic distance distribution. We then generated 500 synthetic networks from the posterior predictive distribution.
\begin{algorithm}[H]
	\spacingset{1}
	\caption{Generate new data for PPC}
	\begin{algorithmic}
		\STATE \textbf{Input}: number of new data to generate $R$,\\
		estimated latent variables $(\boldsymbol{u}, \boldsymbol{b}, \boldsymbol{\eta},  \sigma_\tau^2)$\\
		\vskip 0.1in

		\FOR{$r=1$ {\bfseries to}  $R$}
		\FOR{$d = 1$ {\bfseries to}  $D$} 
		\STATE  Compute $\boldsymbol{x}_{d}$ and $\boldsymbol{y}_{d}$ given $\{(a_{d}, \boldsymbol{r}_{d}, t_{d})\}_{[1:(d-1)]}$
		\STATE	Draw ($a_{d}$, $\boldsymbol{r}_{d}$, $t_{d}$) following Section \ref{sec:generative process}\\
		\ENDFOR
		\STATE Store every $r^{th}$ new data $\{(a_{d}, \boldsymbol{r}_{d}, t_{d})\}_{d=1}^D$ 
		\ENDFOR
	\end{algorithmic}
\end{algorithm}

>>>>

\subsection{Posterior Predictive Checks}\label{subsubsec:PPC_email} 	   
Finally, we perform posterior predictive checks \cite{rubin1984bayesianly} to evaluate the appropriateness of our model specification for the Montgomery County email data and the threat and imposition of sanctions (TIES) data. We formally generated entirely new data, by simulating ties and timestamps $\{(a_{d}, \boldsymbol{r}_{d}, t_{d})\}_{d=1}^D$ from the genenerative process in Section \ref{sec:generative process}, conditional upon a set of inferred parameter values from the inference in Section \ref{sec:inference}. For the test of goodness-of-fit in terms of network dynamics, we use multiple network statistics that summarize meaningful aspects of the Montgomery County email data and the threat and imposition of sanctions (TIES) data: indegree distribution, outdegree distribution, recipient size distribution, time-increments distribution, the edgewise shared partner distribution, and the geodesic distance distribution. We then generated 500 synthetic networks from the posterior predictive distribution.
\begin{algorithm}[H]
	\spacingset{1}
	\caption{Generate new data for PPC}
	\begin{algorithmic}
		\STATE \textbf{Input}: number of new data to generate $R$, covariates $\boldsymbol{x}$ and $\boldsymbol{y}$\\
		estimated latent variables $(\boldsymbol{u}, \boldsymbol{b}, \boldsymbol{\eta},  \sigma_\tau^2)$\\
		\vskip 0.1in

		\FOR{$r=1$ {\bfseries to}  $R$}
		\FOR{$d = 1$ {\bfseries to}  $D$} 
		\STATE	Draw ($a_{d}$, $\boldsymbol{r}_{d}$, $t_{d}$) following Section \ref{sec:generative process}\\
		\ENDFOR
		\STATE Store every $r^{th}$ new data $\{(a_{d}, \boldsymbol{r}_{d}, t_{d})\}_{d=1}^D$ 
		\ENDFOR
	\end{algorithmic}
\end{algorithm}
